%!TEX program = lualatex

\documentclass[9pt, oneside]{memoir}
\setlrmarginsandblock{0.5in}{6in}{*}
\setulmarginsandblock{0.5in}{0.5in}{*}


\usepackage[colorlinks=true]{hyperref}

\setlength{\sidebarhsep}{0.5in}
\setlength{\sidebarwidth}{5in}
\setsidebarheight{\textheight}

\checkandfixthelayout
\setlength{\parindent}{0pt}
\nonzeroparskip

\renewcommand{\sidebarfont}{
    \scriptnotesize
    \nonzeroparskip}
    
\setcounter{secnumdepth}{0}
\setsubsubsecheadstyle{\normalsize\itshape}
\setsubsecheadstyle{\normalsize\bfseries}

\newcommand{\ruledsec}[1]{
    \Large\bfseries #1 \par\vskip-2mm
    \rule{1in}{0.1mm}
    \par\vskip-2mm}
\setsecheadstyle{\ruledsec}

\newcommand{\position}[2]{\subsubsection{#1
    \hfill
    #2}}
    
\usepackage{fontspec}
\setmainfont{carlito}
%\usepackage[top=1cm,bottom=1cm,scale=0.5]{geometry}
\usepackage[scaled=.5]{helvet}
\usepackage{courier}
\setSingleSpace{0.9}
\SingleSpacing

\pagestyle{empty}

    \begin{document}

\begin{minipage}[t][0in][b]{4in}
    {\fontsize{12pt}{8pt}\selectfont
        \rmfamily\textbf{Foly S. Ananou}}\\
\\
{\fontsize{8pt}{8pt}\selectfont
        \rmfamily ananou.foly@icloud.com\\ Phone: +33 6 50 39 62 44}
          \vfill
\end{minipage}


\sidebar{
\section{Work experience}

\subsection{Research and teaching fellow}
\position{Laboratoire d'Analyse et de Prospective Economiques de l'Université de Limoges}{10/2017 -- Present}

\begin{itemize}
\item Drafted research projetcs, and identified testable hypothesis in the fields of macroeconomics, finance and banking
\item Collected, managed and prepared financial and economic data for statistical analysis 
\item Performed statistical and econometric analysis work with R, Stata,  Excel or Python, and write reports summarizing the results
\item  Presented the results of my research at different conferences and workshops
\item  Contributed to peer-reviewing of several economic research .
\item  Participated in funded research projects by the French National Research Agency (ANR CaLiBank project)
\item Elaborated and delivered tutorials in Statistics and Macroeconomics for undergraduate students 
\item Mentored first year graduate level students for the preparation of research dissertations and economic analysis reports

\end{itemize}



\subsection{Economist, Consultant}
\position{Groupe Orange}{01/2017 -- 06/2017}
%\small{
\begin{itemize}
\item Developped, within a team of four members, a method to assess the economic impact of mobile-money in French-speaking West Africa and proposed strategies
to optimize the performance of mobile-banking within that region
\end{itemize}
%}

\subsection{Principal Economist}
\position{French Embassy in Senegal}{07/2012 -- 08/2016}
%\small{
\begin{itemize}
\item Conducted economic analysis and prepared reports on selected topics including developments in exchange rate, inflation and economic growth in Senegal, Cabo Verde, Gambia, and Guinea Bissau
\item Prepared reports, studies and forecasts on major and significant utility issues using statistical and economic analysis techniques.
\item Assessed the socio-economic impact of AFD projects in Senegal, Cabo Verde, Gambia, and Guinea Bissau
\item Developped a country risk assessment methodology based on variables such as inflation, growth and debt levels as well as socio-
economic indicators
\item Carried out statistical and econometric analysis work with R, Stata or Excel and write reports summarizing results to help improve understanding of trade trends in West African countries
\item Provided economic information to the Ambassador's office, other department of the Embassy, and corporations locally presented in West Africa or prospecting 
\item Compiled key government sources of economic information and made them available to the Economic Department team.

\item Others: Builded a database for economic and financial monitoring. Animated the French business community. Monitored trainees.
\end{itemize}
%}

\subsection{Economist, Consultant}
\position{Office of the Prime Minister of the Republic of Benin}{08/2015 -- 12/2015}
%\small{
\begin{itemize}
\item Authored, within a team of five members, two policy notes on financial absorption and youth employment in Benin
\end{itemize}
%}

\subsection{Visiting lecturer}
\position{Ecole Nationale de Statistiques et d'Analyse Economique/Senegal}{09/2013 -- 06/2016}
%\small{
\begin{itemize}
\item Lectured graduate level students (M.Sc. in Statistics and Ecomomic) on Panel data Econometrics
\end{itemize}

}
\sidebar{

\section{Additional activities}
\subsection{Associate Director}

\position{Think tank l'Afrique des Idées}{07/2013 -- Present}
%\small{
\begin{itemize}
\item Directed the economic research program of the think tank L'Afrique des Idées
\item Coordinated team activities and assigned duties for research projects.
\item Gathered empirical data and conducted economic research on topic such as fiscality, monetary union, mobile-banking, and inequality
\item Several media intervention to present and discuss research outcomes

\end{itemize}
}
 


\sidebar{
 
\section{Selected publications}
%\small{
\begin{itemize}
\item \textit{Liquidity regulation and bank lending}, with D. Chronopoulos, A. Tarazi, and J. Wilson. Journal of Corporate Finance, 69(C), 2021.
\item \textit{Liquidity regulation and bank risk.}, with D. Chronopoulos, A. Tarazi, and J. Wilson, 2021. 
\item  \textit{Exploring the dynamic of the tax gap in Africa}, with G. V. Houngbonon, 2017. 
    \item \textit{Agenda pour une réforme du Franc CFA}, with B. Houenou, G.V. Houngbonon, D. Ouedraogo, B. Sandwidi, and J.K. Tchangai. L'Afrique des Idées, January 2019. 
    \item \textit{Mobilisation des recettes fiscales en Afrique: L'obstacle de l'informel, le levier du mobile-money}, with B. Houenou, G.V. Houngbonon, and O. Gandzion. L'Afrique des Idées, July 2017. 
    \item \textbf{The Conversation France} -- \textit{Collecte-t-on trop ou trop peu d’impôts en Afrique ?}
    \item \textbf{Jeune Afrique} -- \textit{Il est temps de penser à l’après-Franc CFA !}
\item Authors of several notes and economic analysis report, available at \href{https://www.lafriquedesidees.org/?s=foly+ananou}{lafriquedesidees.org/?s=foly+ananou}
\end{itemize}
%}
}

\sidebar{
 
%\end{describe}

}

\sidebar{
 
}

    \section{Education}
    \position{PhD, Economics\\\emph{Univ. de Limoges}}{2021}
    \position{M.Phil., Economics\\\emph{Univ. de Limoges}}{2017}
    \position{M.Sc., Econ. and Statistics\\\emph{ENSAE-Senegal}}{2012}
    \position{B.Sc., Statistics\\\emph{ENSAE-Senegal}}{2010}

    \section{Languages}
\position{French}{Native}
\position{English}{Fluent}

   \section{IT Skills}
\position{\emph{Most recently used:}}{Stata, Ms Office, Latex}
\position{Proficient:}{Stata, Eviews, Ms Office, LateX, Bloomberg}  
 \position{Competent:}{CsPro, VBA, SQL, R, Python}
    % \position{Familiar:}{    R, Python}
%}

%}


%}


   \section{Non-IT Skills}
%\begin{describe}
     Economic and econometric modeling $\bullet $  Data analysis $\bullet $ Banking and Finance $\bullet $ Economic and policy analysis $\bullet $  Critical thinking $\bullet $  Machine Learning  $\bullet $ Program management
$\bullet $ Teamwork
$\bullet $ Reliability $\bullet $ Organization
$\bullet $ Public Speaking 

   \section{Grants and Awards}
%\begin{describe}
 \emph{Bureau Van Dijk Prize for the best paper in Banking}, 34th AFBC Sydney, 14-17 December 2021 $\bullet $ \emph{French Doctoral Fellowship}, awarded in 2017 $\bullet $ \emph{Université de Limoges Excellence Scholarship for International Students}, awarded in 2016 $\bullet $ \emph{Odon Vallet Scholarship, Ensae-Senegal}, awarded 2006--2012. 

%\end{describe}



\end{document}